Prag Bat

### 2020-02-21 analysis/data_processing.Rmd
update models

log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
         id = paste("Vp",`ID `, sep = ""))%>%
  select(id, age, status)

data <- task_data %>%
  left_join(log)%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
         subage = as.numeric(substr(age,1,1)),
         trial = as.numeric(trial))%>%
  select(-test_date, - status, -check_age)%>%
  mutate(trial = ifelse(test_day == "2", 
                        ifelse(task == "card_sorting", trial + 6, trial +5),
                        trial),
         z_age = age - mean(age),
         z_trial = trial - mean(trial))

@@

card_sorting_model_data <- card_sorting_data %>%
  mutate(trial = trial - mean(trial))

card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = card_sorting_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model1.rds")

card_sorting_model2 <- brm(correct ~ trial + (trial|id),
                    data = card_sorting_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model2.rds")

@@

inf_model_data <- inf_data %>%
  mutate(trial = trial - mean(trial))

# inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = inf_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/inf_model1.rds")
# 
# inf_model2 <- brm(correct ~ trial + (trial|id),
#                     data = inf_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/inf_model2.rds")

@@

me_model_data <- me_data %>%
  mutate(trial = trial - mean(trial))

# me_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = me_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/me_model1.rds")
# 
# me_model2 <- brm(correct ~ trial + (trial|id),
#                     data = me_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/me_model2.rds")

@@

nov_model_data <- nov_data %>%
  mutate(trial = trial - mean(trial))

# nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = nov_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/nov_model1.rds")
# 
# nov_model2 <- brm(correct ~ trial + (trial|id),
#                     data = nov_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/nov_model2.rds")

@@

pref_model_data <- pref_data %>%
  mutate(trial = trial - mean(trial))

# pref_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = pref_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/pref_model1.rds")
# 
# pref_model2 <- brm(correct ~ trial + (trial|id),
#                     data = pref_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/pref_model2.rds")

@@

x <- bind_rows(
  posterior_samples(card_sorting_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "1 card_sorting"),
  posterior_samples(inf_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "4 informativeness"),
  posterior_samples(nov_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "2 novelty"),
  posterior_samples(me_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "3 mutual_exclusivity"),
  posterior_samples(pref_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "0 preference")
)%>%
  gather(estimate, value, -task)

@@

## card sorting
samples_cs <- posterior_samples(card_sorting_model1, "^b")%>%
  mutate(sample = 1:length(b_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "card_sorting")

## informativeness
samples_inf <- posterior_samples(inf_model1, "^b")%>%
  mutate(sample = 1:length(b_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "informativeness")

>>>>

log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
         id = paste("Vp",`ID `, sep = ""))%>%
  select(id, age, status)

data <- task_data %>%
  left_join(log)%>%
  filter(status == "keep")%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
         subage = factor(as.numeric(substr(age,1,1))),
         trial = as.numeric(trial))%>%
  select(-test_date, - status, -check_age)%>%
  mutate(trial = ifelse(test_day == "2", 
                        ifelse(task == "card_sorting", trial + 6, trial +5),
                        trial),
         z_age = age - mean(age),
         z_trial = trial - mean(trial))

@@

card_sorting_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
                    data = card_sorting_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model1.rds")

card_sorting_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
                    data = card_sorting_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model2.rds")

@@

inf_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
                    data = inf_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model1.rds")

inf_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
                    data = inf_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model2.rds")

@@

me_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model1.rds")

me_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model2.rds")

@@

nov_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
                    data = nov_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model1.rds")

nov_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
                    data = nov_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model2.rds")

@@

pref_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
                    data = pref_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/pref_model1.rds")

pref_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
                    data = pref_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/pref_model2.rds")

@@

x <- bind_rows(
  posterior_samples(card_sorting_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "1 card_sorting"),
  posterior_samples(inf_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "4 informativeness"),
  posterior_samples(nov_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "2 novelty"),
  posterior_samples(me_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "3 mutual_exclusivity"),
  posterior_samples(pref_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "0 preference")
)%>%
  gather(estimate, value, -task)

@@

## card sorting
samples_cs <- posterior_samples(card_sorting_model1, "^b")%>%
  mutate(sample = 1:length(b_z_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "card_sorting")

## informativeness
samples_inf <- posterior_samples(inf_model1, "^b")%>%
  mutate(sample = 1:length(b_z_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "informativeness")
